DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-05 Draft Ped Metrics Example.Rmd
changes the main breakdowns to non city county roads

cities <- sf::read_sf(paste0(this_dir,"data/cities"))
uga <- sf::read_sf(paste0(this_dir,"data/uga"))
uga$isuga = 1
lamird <- sf::read_sf(paste0(this_dir,"data/lamird"))
lamird$islamird = 1
community <- sf::read_sf(paste0(this_dir,"data/community"))

@@

# need to make sure that this is right
ncdf <- road_df[!lengths(st_intersects(road_df, cities)), ] %>%
  mutate(LENGTH = as.integer(st_length(.)))

#cdf <- st_intersection(road_df, cities)
#ncdf2 <- st_as_sf(road_df) %>%
#  mutate(rdseg = paste(SEGMENT_ID, RD_LOG_ID)) %>%
#  filter(rdseg %ni% mutate(cdf,rdseg = paste(SEGMENT_ID, RD_LOG_ID))$rdseg)
```

@@

sidewalks_nc <- sidewalks[!lengths(st_intersects(sidewalks, cities)), ]%>% 
  st_as_sf(.) %>%
  filter(WIDTH > 0, LENG_FT > 0) %>%
  mutate(LENGTH = as.integer(st_length(.)),
         TYPE = paste0("Sidewalk: ",WIDTH, " ft"),
         RD_LOG_ID = as.integer(ROADLOGID),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH, LENGTH, TYPE)
shoulders_nc <- shoulders[!lengths(st_intersects(shoulders, cities)), ] %>% 
  st_as_sf(.) %>%
  filter(SHLDR_WIDT > 0, SHLDR_SURF == "ACP", DISTANCE_F > 0) %>%
  mutate(LENGTH = as.integer(st_length(.)),
         TYPE = paste0("Paved Shoulder: ", SHLDR_WIDT," ft"),
         RD_LOG_ID = as.integer(ROAD_LOG_I),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH = SHLDR_WIDT, LENGTH, TYPE)
nc_sw_sh <- bind_rows(sidewalks_nc, shoulders_nc)

@@

knitr::kable(
 # ncdf_w_all_nogeo %>%
  comb_score %>%
  group_by(setting, road_class, score) %>% 
  summarise(roads = nice_comma(n_distinct(RD_LOG_ID_R)), 
            segments = nice_comma(n()), 
            #length = nice_comma(sum(LENGTH, na.rm=TRUE)/5280, 1),
            dist = nice_comma(sum(distance, na.rm=TRUE)/5280, 1),
            .groups = "drop") 
  )
```

>>>>

cities <- sf::read_sf(paste0(this_dir,"data/cities"))

# try to make a kitsap without cities
county_no_cities <- st_difference(outline, st_union(cities))

uga <- sf::read_sf(paste0(this_dir,"data/uga"))
uga$isuga = 1
lamird <- sf::read_sf(paste0(this_dir,"data/lamird"))
lamird$islamird = 1
community <- sf::read_sf(paste0(this_dir,"data/community"))

@@

# need to make sure that this is right

ncdf <- st_intersection(road_df, st_buffer(county_no_cities,0)) %>%
  mutate(LENGTH = as.integer(st_length(.)))

@@

sidewalks_nc <- st_intersection(sidewalks, st_buffer(county_no_cities,0)) %>%
  st_as_sf(.) %>%
  filter(WIDTH > 0, LENG_FT > 0) %>%
  mutate(LENGTH = as.integer(st_length(.)),
         TYPE = paste0("Sidewalk: ",WIDTH, " ft"),
         RD_LOG_ID = as.integer(ROADLOGID),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH, LENGTH, TYPE)
shoulders_nc <- st_intersection(shoulders, st_buffer(county_no_cities,0)) %>%
  st_as_sf(.) %>%
  filter(SHLDR_WIDT > 0, SHLDR_SURF == "ACP", DISTANCE_F > 0) %>%
  mutate(LENGTH = as.integer(st_length(.)),
         TYPE = paste0("Paved Shoulder: ", SHLDR_WIDT," ft"),
         RD_LOG_ID = as.integer(ROAD_LOG_I),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH = SHLDR_WIDT, LENGTH, TYPE)
nc_sw_sh <- bind_rows(sidewalks_nc, shoulders_nc)

@@

knitr::kable(
  comb_score %>%
  group_by(setting, road_class, score) %>% 
  summarise(roads = nice_comma(n_distinct(RD_LOG_ID_R)), 
            segments = nice_comma(n()), 
            dist = nice_comma(sum(distance, na.rm=TRUE)/5280, 1),
            .groups = "drop") 
  )
```
